\vspec{} and Friends: A suite of utilities to model spectroscopic phase curves of 3D exoplanet atmospheres in the presence of stellar variability.

### 2024-07-23 src/tex/ms.tex
Add Gridpolator section and update scripts

\TJ{TODO}

>>>>

\vspec{} pulls its stellar spectral models from a library of pre-computed stellar models. Detailed stellar spectral models are computationally expensive to generate, so it is more efficient to interpolate over a descritized grid. This interpolation is handled by the Python package GridPolator, whose main class \texttt{GridSpectra} acts as a wrapper for the SciPy or JAX \TJ{(refs?)} \texttt{RegularGridInterpolator} with a specialized API. This setup allows spectral grids of arbitrary dimension, and treats the wavelength axis independently of the other parameters so that each wavelength channel is independent. When a \texttt{Gridspectra} instance's \texttt{evaluate()} method is called it creates a \texttt{RegularGridInterpolator} instance for each wavelength channel, evaluates that interpolator, and then resamples the returned spectrum at the requested wavelength points. In the case that the JAX implementation is used, the portion of \texttt{evaluate()} that does the interpolation is just-in-time (JIT) compiled to dramatically improve performance on subsequent calls.

GridPolator grids can be built arbitrarily by the user, but the package comes with two built-in grids. The first\footnote{The raw spectra are hosted on Zenodo: \url{https://zenodo.org/records/10429325}} was created by Peter Hauschildt \TJ{(Private communication? He has said he does not feel authorship is warranted.)} using \texttt{PHOENIX} stellar models \citep{allard1994,hauschildt1999,husser2013}. Each spectrum spans from 0.1 to 20 microns in steps of $5\times10^{-6}$ microns. The stellar atmospheres used to create the spectra have solar metallicity and a $\log{g}$ of 5.0, with effective temperatures ranging from 2300K to 3900K in steps of 100K. This is the only grid currently supported by \vspec{}, with support for more grids planned in future releases. The second grid is hosted by the Space Telescope Science Institute\footnote{\url{https://archive.stsci.edu/hlsps/reference-atlases/cdbs/grid/phoenix/}}. This grid covers a much larger stellar parameter space, with metallicities ranging from $-4$ to $0.5$, \teff from 2000K to 70\,000K, and $\log{g}$ from 0 to 5.5. These models are also produced by the \texttt{PHOENIX} code. Except for the solar metallicity models, the spectra were computed in 2011 by \citet{allard2003, allard2007} and the solar metallicity models were updated by a new version of \texttt{PHOENIX} in 2021 \citep{allard2012}. \TJ{Look up wavelength ranges}

When either of the two above grids are initialized, GridPolator looks for the relevant data files on the user's local system. If they are not present, then the files are downloaded and stored in \texttt{\~/.gridpolator/grids/}

Within this suite of codes, GridPolator has the added responsibility of binning spectra and producing wavelength axes that match those output by PSG. Wavelength sampling is done using constant resolving power $R=\frac{\lambda}{\Delta \lambda}$. The binning algorithm takes a pair of high resolution flux and wavelength arrays and resamples the flux to a lower resolution wavelength axis. This algorithm assumes that each point on the new wavelength axis is the central value of the wavelength channel \TJ{(I have never liked this, should I rewrite it before publication?)}.
